---
title: "RStudio"
author: "James Ware"
date: "22 April 2015"
output: ioslides_presentation
#output: pdf_document
#output: word_document
---

##Topics

- knitr / rmarkdown for reproducible documents
- version control (git/svn)
- R packages

RStudio makes these easy(er)

## R Markdown

This presentation is produced from an R Markdown document.  
Markdown is a simple formatting syntax for authoring documents.  It is designed to be simple & legible in plain text editors, but can be rendered as HTML, PDF or MS Word.  
For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

R-flavored markdown also lets you embed and evaluate code:

## Data

```{r}
# define new data
LV_EF <- c(rnorm(19,40,2),5)
LV_EDD <- rnorm(20,55,5)
head(LV_EF)
head(LV_EDD)
```

```{r, include=FALSE}
outlierComment <- "Now let's deal with that outlier"
```


```{r,include=FALSE,eval=FALSE}
#Sample 20 was a catastrophe: remove it:
LV_EF <- LV_EF[-20]
LV_EDD <- LV_EDD[-20]
outlierComment <- "Outlier gone"
```

we analysed `r length(LV_EF)` samples

## You can also embed plots

```{r, echo=FALSE}
boxplot(LV_EF,main="LVEF",horizontal=T)
```

You can control whether the R code is displayed: here it is suppressed, and only output shown.

## LVEF does not correlate with LV EDD

```{r, echo=FALSE}
plot(LV_EF,LV_EDD)
```

`r outlierComment`

## LVEF does not correlate with LV EDD
Other output formats

## Version control: RStudio has native support for Git / GitHub & Subversion.
Brief demo:

- commit / push / pull
- checkout a repo

## R packages provide self-contained container to distribute code and/or data
There is a standard layout of directories
- /R
- DESCRIPTION
- NAMESPACE
- .Rproj (needed to get full benefits of RStudio, e.g. github, autosaving)
- (/data)

I use package-like directory tree for all R projects (even if not packages)

http://r-pkgs.had.co.nz

## RStudio for package developers
lots of handy shortcuts for building & checking packages  
library(devtools)

## Reproducible science
R markdown for project reports & presentations, and even manuscripts
Git for version control & collaboration
Packages for distribution (or Git repos)