---
title: "Reproducible science in R: handy tools"
#subtitle: "RStudio, Rmarkdown, git, packages"
author: "James Ware"
date: "22 April 2015"

output: ioslides_presentation
#output: pdf_document
#output: word_document
#output: beamer_presentation
---

##Topics

- knitr / rmarkdown for reproducible documents
- version control (git/svn)
- R packages

RStudio makes these easy(er)

## R Markdown

This presentation is produced from an R Markdown document.  
Markdown is a simple formatting syntax for authoring documents.  It is designed to be simple & legible in plain text editors, but can be rendered as HTML, PDF or MS Word.  
For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

R flavored markdown also lets you embed and evaluate code:

## Data

```{r}
# define new data
LV_EF <- signif(c(rnorm(19,40,2),5),3)
LV_EDD <- signif(rnorm(20,55,5),3)
head(LV_EF)
head(LV_EDD)
```

```{r, include=FALSE}
outlierComment <- "Now let's deal with that outlier"
```


```{r,include=FALSE}
#Sample 20 was a catastrophe: remove it:
# LV_EF <- LV_EF[-20]
# LV_EDD <- LV_EDD[-20]
# outlierComment <- "Outlier gone"
```

**Text for a manuscript**  
We analysed `r length(LV_EF)` samples. Mean LV EF was `r signif(mean(LV_EF),3)`.

## You can also embed plots

```{r, echo=FALSE}
boxplot(LV_EF,main="LVEF",horizontal=T)
```

You can control whether the R code is displayed: here it is suppressed, and only output shown.

## A table

```{r, echo=FALSE, warnings=F,results='asis'}
knitr::kable(head(data.frame(LV_EF,LV_EDD)))
```


## LVEF does not correlate with LV EDD

```{r, echo=FALSE}
plot(LV_EF,LV_EDD)
abline(lm(LV_EDD ~ LV_EF),col="red")
```

`r outlierComment`

## R markdown
Demonstrate other output formats

- html document, ioslides
- pdf document, beamer slides
- word docx

all can be customized with appropriate templates etc

## Version control: RStudio has native support for Git / GitHub & Subversion.
Brief demo:

- commit / push / pull
- checkout a repo
    + git@github.com:jamesware/denovolyzerManuscript.git
    + manuscriptDemo

## R packages: a container to distribute code and/or data
Standard directory layout:

- /R
- DESCRIPTION
- NAMESPACE
- .Rproj (needed to get full benefits of RStudio, e.g. github, autosaving)
- (/data)

I use package-like directory tree for all R projects (even if not packages)

http://r-pkgs.had.co.nz

## RStudio for package developers
lots of handy shortcuts for building & checking packages  
devtools
roxygen

(look at denovolyzeR for example if time)

## Reproducible science

- R markdown for project reports & presentations, and even manuscripts  
- Git for version control & collaboration  
    + https://github.com/macarthur-lab/exac_papers
- Packages for distribution (or Git repos)  